This document will be filled out with code to run MCMC on a model, just using R functions. The core parts are:

 * the likelihood function
 * the prior density function
 * the posterior density function
 * the MCMC sampler

## the problem

We'll be writing a model for the Polis logistic regression model, which models (observed) occupancy of a species at islands, as a function of the perimeter/area ratio of the island. The JAGS version is in `H.LogisticRegPolis.Rmd`. Here's the data again:

```{r data}
data <- list(
  PA = c(15.41, 5.63, 25.92, 15.17, 13.04, 18.85, 30.95, 22.87, 12.01, 
         11.6, 6.09, 2.28, 4.05, 59.94, 63.16, 22.76, 23.54, 0.21, 2.55),
  Y = c(1, 1, 1, 0, 1, 0, 0, 0, 0, 1, 1, 1, 1, 0, 0, 0, 0, 1, 1)
)
```

The model looks like this in statistical notation:

$$
Y_i \sim Bernoulli(p_i) \\ 
logit(p_i) = a + b  \times \text{PA}_i
$$
and we use these priors (written with the *variance* not the precision):
$$
a \sim N(0, 10^6) \\ 
b \sim N(0, 10^6)
$$
The JAGS code looked like this:
```{r jags}
"
model
{
  a ~ dnorm(0, 1.0E-6)  # priors for regression coefficients
  b ~ dnorm(0, 1.0E-6)

  # for each of the 19 islands
  for (i in 1:19)
  {
    logit(p[i]) <- a + b * PA[i]   # calculate the probability of occupancy
    Y[i] ~ dbern(p[i])          # randomly draw the actual occupancy from a Bernoulli distribution
    # PA2[i] <- PA[i] - mean(PA[1:19])
  }
}
"
```

## the likelihood function

```{r likelihood}
likelihood <- function (params, data) {
  
  a <- params[1]
  b <- params[2]

  logit_p <- a + b * data$PA
  p <- plogis(logit_p)
  lp <- dbinom(data$Y, 1, p, log = TRUE)
  sum(lp)
}
```

## the prior density function

```{r prior}
prior <- function (params) {
  a <- params[1]
  b <- params[2]
  lp_a <- dnorm(a, 0, 1000, log = TRUE)
  lp_b <- dnorm(b, 0, 1000, log = TRUE)
  lp_a + lp_b
}
```

## the posterior density function

```{r posterior}
posterior <- function(params, data) {
  prior(params) + likelihood(params, data)
}
```

## the MCMC algorithm

Specifically, this is for the random walk Metropolis-Hastings sampler

```{r proposal}
propose <- function (params, step_size = 10) {
  a <- params[1]
  b <- params[2]

  step_a <- rnorm(1, 0, step_size)
  step_b <- rnorm(1, 0, step_size)
  new_location <- c(a + step_a,
                    b + step_b)
}
```


```{r acceptance}
accept <- function (params_new, params_old, data) {
  
  lp_old <- posterior(params_old, data)
  lp_new <- posterior(params_new, data)
  
  log_diff <- lp_new - lp_old
  log(runif(1)) < log_diff
}
```

```{r sampler}
rwmh <- function (inits, data, n_iter = 1000, step_size = 10) {
  
  trace <- matrix(NA, n_iter, 2)
  params_old <- inits
  
  for (iter in 1:n_iter) {
    
    # print(paste("mcmc iteration", iter))
    
    params_new <- propose(params_old, step_size = step_size)
    accepted <- accept(params_new, params_old, data)
    
    if (accepted) {
      params_old <- params_new
    }
    
    trace[iter, ] <- params_old
    
  }
  
  trace
  
}
```

## run the algorithm on the data

```{r get_samples}

draws <- rwmh(inits = c(-3, 1), data, n_iter = 100000, step_size = 0.7)

```
```{r plot}
par(mfrow = c(2, 1))
plot(draws[, 1], type = "l", ylab = "a")
plot(draws[, 2], type = "l", ylab = "b")

```

